\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Updated state of the art sections
Moved EEG/fMRI to intro

Eye tracking provides unprecedented access to the users' attention and
engagement during interactive scenarios. Previous research has shown
that gaze data can be used as a proxy to understand the underlying
socio-cognitive aspects in not only human-computer interaction but in
human-human interaction as well. In the present decade, off the shelf
eye-trackers have become readily available to the researchers to assess
the users' attention and engagement.

On the other hand, educational robots can be of great use in making young school
kids interested in technological developments~\cite{cooper1999robots,
wyffels2010building}. It is important to know about the key socio-cognitive
features of this subset of human-robot interaction because these features let
the researchers design better interactive scenarios in the future. These
features include the conceptual mapping of the sensor data visualisation and the
robot's function and the generalising the concepts to solve a given problem in a
contextual learning environment. ~

@@

We present a study with combining eye tracking and human robot interaction (HRI)
in an educational setting. ~Eye tracking data is of high temporal precision as
compared to some of the physiological data sources such as fMRI or other
biometric devices used to measure the palpitation and the body temperature. The
eye tracking devices are portable enough as opposed to the bulky apparatus used
in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
access to the users' attention than other portable and physiological data
sources such as EEG; this makes eye-tracking data a pertinent source to measure
attention.

@@

@@

@@

@@

@@

\section{Eye Tracking as a Tool for Assessing Social Interaction}

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an eye-tracking
study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation.

\section{Method Description}

\subsection{Gaze measures}

The most common form of eye-tracking data aggregation are the fixations.
Fixations depict the periods in the user's observation when the user
attends a relatively small part of the visual stimulus for a relatively
longer period of time. The various fixation detection algorithms are
summarised in~\cite{duchowski2007eye}. Following are the two gaze measures, derived
from the fixations, which we used in the present work.

\section{Field of Application and Deployment}

@@

\begin{enumerate}
\item Fixaitons
\item Saccades and transitions
\item Smooth Persuite
\item Areas of Interest
\item Heatmaps

@@

@@

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.
\section{Conclusion}

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to analyse HRI situations. The prime advantage of using
mobile eye-tracking is that the users' interaction with the robot can
still be ecologically valid. On the other hand, using fMRI for
evaluating HRI reduces the interaction to a video of the robot only
~\cite{rosenthal2013neural}.

>>>>

Eye tracking provides unprecedented access to the users' attention and
engagement during interactive scenarios. Previous research\fixme{refs} has shown
that gaze data can be used as a proxy to understand the underlying
socio-cognitive aspects in not only human-computer interaction but in
human-human interaction as well. In the present decade, off the shelf
eye-trackers have become readily available to the researchers to assess
the users' attention and engagement.

On the other hand, educational robots can be of great use in making young school
kids interested in technological developments~\cite{cooper1999robots,
wyffels2010building}. It is important to know about the key socio-cognitive
features of this subset of human-robot interaction because these features let
the researchers design better interactive scenarios in the future. These
features include the conceptual mapping of the sensor data visualisation and the
robot's function and the generalising the concepts to solve a given problem in a
contextual learning environment.

@@

\paragraph{Biometric Measurements of Interaction}

\fixme{organize/rewrite this paragraph}

\fixme{Mention skin conductance as well}

@@

Eye-tracking data is of high temporal precision as
compared to some of the physiological data sources such as fMRI or other
biometric devices used to measure the palpitation and the body temperature. The
eye tracking devices are portable enough as opposed to the bulky apparatus used
in fMRI~\cite{rosenthal2013neural}.  Eye tracking data provides more direct
access to the users' attention than other portable and physiological data
sources such as EEG; this makes eye-tracking data a pertinent source to measure
attention.

The prime advantage of using mobile eye-tracking is that the users' interaction
with the robot can still be ecologically valid. On the other hand, using fMRI
for evaluating HRI reduces the interaction to a video of the robot only
~\cite{rosenthal2013neural}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Eye Tracking as a Tool for Assessing Social Interaction}

\subsection{Gaze patterns and Collaborative work}

@@

Controlling robot with gaze

@@

It must be noted that to our best knowledge only very few studies have
investigated how eye-tracking could be used to assess HRI. In an eye-tracking
study, in the context of human robot interaction, \cite{staudte2009visual} found
that when the robot provides a matching visual and verbal reference to an object
the participants were more likely to look at the correct objects. This result
was consistent irrespectively of the ambiguity of the situation. 
SAY ABOUT THE VIDEO BASED INTERACTION

@@

\section{Method description}

@@

\begin{enumerate}
\item Fixations: The most common form of eye-tracking data aggregation are the fixations.
Fixations depict the periods in the user's observation when the user
attends a relatively small part of the visual stimulus for a relatively
longer period of time. The various fixation detection algorithms are
summarised in~\cite{duchowski2007eye}.

\item Saccades and transitions
\item Smooth Pursuit
\item Areas of Interest
\item Heat-maps

@@

\subsection{Eye-tracking measures}

@@

%Another plausible explanation for the participants in {\sf NONE} and {\sf RANDOM} condition
%being better performers than the {\sf TRUE} condition during the interaction phase
%comes from the transparency of the robot's behaviour. The robot's
%behaviour was not at all transparent in the former two conditions. This might
%have caused the participants to put more effort in understanding the behaviour.
%Therefore, they performed better.

\section{Conclusion}

We demonstrated that eye-tracking data can provide several process
variables to assess not only the task-based performance of the
participants but also to analyse HRI situations.
